---
title: "hw08"
author: "DUONI FU"
date: "2017Äê11ÔÂ4ÈÕ"
output: 
   md_document:
      variant: markdown_github
   html_document: null
---

## 1.
a) OpenWeatherMap, a global geospatial platform provides earth observation data including current, historical and forcasting weather data, map layer data as well as air pollution data. The data I want to use in this assignment is the historical UV index data.
b) OpenWeatherMap <https://openweathermap.org/api>  
OpenWeatherMap-UV <https://openweathermap.org/api/uvi>
c) base URL endpoint: <http://api.openweathermap.org/data/2.5/uvi/history?>
```http://api.openweathermap.org/data/2.5/uvi/history?appid={appid}&lat={lat}&lon={lon}&cnt={cnt}&start={start}&end={end}```

## 2.
a) There are five levels of API, Free, Startup, Developer, Professional and Enterprise. The calls per minute and access to some databases are limited for free account. To get a free account, just sign up.
b) Apply for an API key by signing up for a free account <https://home.openweathermap.org/users/sign_up>

## 3.
a) 
```{r}
library(httr)
endpoint= "http://api.openweathermap.org/data/2.5/uvi/history?"
key=Sys.getenv("OWM_APP_TOKEN")
lat="40.0"
lon="-74.0"
start="1498049953"
end="1508644800"
url=paste(endpoint,"lat=", lat, "&lon=", lon, "&start=", start, "&end=", end, "&appid=", key, sep="")
query=GET(url)
```
the parameter: lat means latitude, lon means longitude, start and end mean the starting and final point of time period in UNIX time. This query requests the UV index data from 2017/6/22 to 2017/10/22 in New York (40, -74).

b) 
```{r}
http_status(query)
```

c) 
```{r}
http_type(query)
```
## 4.
a) 
```{r}
library(jsonlite)
data=fromJSON(url, simplifyDataFrame = TRUE)
```

b) 
```{r}
head(data)
dim(data)
summary(data$value)
saveRDS(data, "data.rds")
```
## 5.
```{r}
GetSearchResults <- function(lat="40", lon="-74", start="1498049953", end="1508644800"){
  library(httr)
  endpoint= "http://api.openweathermap.org/data/2.5/uvi/history?"
  key=Sys.getenv("OWM_APP_TOKEN")
  url=paste(endpoint,"lat=", lat, "&lon=", lon, "&start=", start, "&end=", end, "&appid=", key, sep="")
  query=GET(url)
  if (http_status(query)$reason!="OK") print(http_status(query)$message)
  else {
    data=fromJSON(url, simplifyDataFrame = TRUE)
    return(data)
  }
}
rds=GetSearchResults()
rds
saveRDS(rds, "api_client_output.RDS")
```

