---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The aim of this project is to collect the profiles of NBA players available on the wiki.
Since it takes time to connect to websites, I only choose the first 50 NBA player on the list to shorten the time.
It obtain information from the wikipedia, clean them, combine them, summarize them and export as rds file.
The variables includes Name, nationality, born, year, High school, college, height, weight, NBA draft, etc.

## data collection

First, I collect the bacis information such as name and nationality of 50 foreign NBA players for the wikipedia page https://en.wikipedia.org/wiki/List_of_foreign_NBA_players.

Then, in order to get more information, I extract players' name from the list and refer to their wiki page, output shows the first 5 links, in form of https://en.wikipedia.org/wiki/firstname_lastname, this process involves cleaning and transforming the data.

With the help of link we got, we can get more information such as born, height, weight... of the players. Result shows the information I get. get_wiki_info function help me obtain and orgainze the data.

Next, I combine two parts of data, clean them and save them as rds.

Finally, I provide some summary statistics of year served, weight and height.

## Discussion

I try to find a API that I can use to find more relative data, however I fail to find a free one, that is a pity.

Another thing is that I do document the package using devtools::document() but it suggests "No man pages found in package  'final' ". I successed the last time but can't try out this time, I am sorry.

And since my data contains some strange names like Juan_Ignacio_Sánchez which have chracter that may not be recognized by computer, it may may go wrong on your computer. I successfully run it on my computer. So if it go wrong on your one, please let me know, I can explain.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
